---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reedsolomon

<!-- badges: start -->
<!-- badges: end -->

The goal of {reedsolomon} is to apply the Reed-Solomon algorithm on remote sensing data. It is based on the work of Werner (2020).

## Installation

You can install the development version of {reedsolomon} from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Nowosad/reedsolomon")
```

## Example

```{r}
library(terra)
s1 = rast(system.file("ex/logo.tif", package = "terra"))
plot(s1)
```

```{r}
library(reedsolomon)
r1 = reedsolomon(s1)
plot(r1)
```

## References

- Werner, P. A. (2020). Application of the Reed-Solomon Algorithm as a Remote Sensing Data Fusion Tool for Land Use Studies. Algorithms, 13(8), 188. MDPI AG. Retrieved from http://dx.doi.org/10.3390/a13080188

## Contribution

Contributions to this package are welcome - let us know if you have any suggestions or spotted a bug. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [an issue](https://github.com/nowosad/bespatial/issues).
